Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-24 paper/paper.tex
detail

% specialization & integration
Concepts on human brain organization have long been torn
between the two extremes
\textit{functional specialization} and \textit{functional integration}.
Functional specialization emphasizes that microscopically distinguishable
brain regions solve distinct classes of computational processes
\cite{kanwisher2010functional}.
Functional integration, in turn, emphasizes that brain function
is enabled by complex connections between these
distinct brain regions \cite{sporns14nn}.
%
These notions were predominantly derived from
invasive examination of anatomy (i.e., histological preparation),
connectivity, (i.e., axonal tracing),
and functional properties
(i.e., single cell recordings) in animals.
Regarding functional segregation into specialized regions,
early histological investigations into the microscopic heterogeneity of
the human cerebral cortex have resulted
in several detailed anatomical maps
\cite{brodmann1909vergleichende, vogt1919allgemeine}.
Regarding axonal connections,
each such cortical area has been observed
to possess a unique set of incoming and outgoing connections
\cite{passingham2002, young93monkey, scannell95cat}.
%
Both
local
%cyto- and chemoarchitectonic
infrastructure
and its unique global connectivity profile
together are thought to realize brain function.
%
In sum,
cortical brain modules versus connections between those
reflect 
functional specialization versus functional integration
\cite{friston2002beyond, mesulam_sensation}.
Importantly,
probably no existing brain analysis method acknowledges that
both architectural principles are inextricably involved
in the realization of mental operations
\cite{tononi1998complexity, saygin2012}.

% SPECIAL
Functional specialization has been
explored and interpreted based on many different research methods.
%
Single cell recordings and microscopic examination
revealed, for instance, the
specialization in the visual cortex into V1, V2, V3, V3A, and V4
\cite{hubel1962receptive, zeki1978functional}.
Tissue lesion of the mid-fusiform gyrus of the visual system,
for instance,
was frequently reported to impair
recognition of others' identity from faces
\cite{iaria2008contrib}.
The whole-brain localization of
sensory, motor, and emotional functions to cortical areas
% in the living brain
has later been enabled by
non-invasive brain imaging with
functional magnetic resonance imaging (fMRI) and
positron emission tomography (PET)
\cite{fristen1997imaging}.
Further,
radioactive mapping of neurotransmitter receptors
rendered accessible yet another
local characteristic of neuronal populations
\cite{zilles2009receptor}.
% allude to our many-regions layer in our methods
In the computational era,
automatic clustering methods are increasingly employed to
regionally differentiate the cerebral cortex,
which can partly be more fine-grained than
classical microscopical borders
\cite{behrens03, cbp2015review}.
Today,
high-thoughput approaches enable
ultahigh-resolution 3D models of brain anatomy
at near-cellular scale
\cite{amunts2013bigbrain}.
%
As a crucial common point,
all these methodological approaches
yield neuroscientific findings
that are naturally interpreted according to
non-overlapping, discrete region compartments
as the basic architecture of brain organization.

>>>>

% specialization & integration
Concepts on human brain organization have long been torn
between the two extremes
\textit{functional specialization} and \textit{functional integration}.
Functional specialization emphasizes that microscopically distinguishable
brain regions solve distinct classes of computational processes
\cite{kanwisher2010functional}.
Functional integration, in turn, emphasizes that brain function
is enabled by complex connections between these
distinct brain regions \cite{sporns14nn}.
%
These notions were predominantly derived from
invasive examination of anatomy (i.e., histological preparation),
connectivity, (i.e., axonal tracing),
and functional properties
(i.e., single cell recordings) in animals.
Regarding functional segregation into specialized regions,
early histological investigations into the microscopic heterogeneity of
the human cerebral cortex have resulted
in several detailed anatomical maps
\cite{brodmann1909vergleichende, vogt1919allgemeine}.
Regarding axonal connections,
each such cortical area has been observed
to possess a unique set of incoming and outgoing connections
\cite{passingham2002, young93monkey, scannell95cat}.
%
Both
local
%cyto- and chemoarchitectonic
infrastructure
and its unique global connectivity profile
together are thought to realize brain function.
%
In sum,
cortical brain modules versus connections between them
reflect 
functional specialization versus functional integration
\cite{friston2002beyond, mesulam_sensation}.
Importantly,
probably no existing brain analysis method acknowledges that
both architectural principles are inextricably involved
in the realization of mental operations
\cite{tononi1998complexity, saygin2012}.

% SPECIAL
Functional specialization has been
explored and interpreted based on many different research methods.
%
Single cell recordings and microscopic examination
revealed, for instance, the
specialization in the visual cortex into V1, V2, V3, V3A, and V4
\cite{hubel1962receptive, zeki1978functional}.
Tissue lesion of the mid-fusiform gyrus of the visual system,
for instance,
was frequently reported to impair
recognition of others' identity from faces
\cite{iaria2008contrib}.
The whole-brain localization of
sensory, motor, and emotional functions to cortical areas
% in the living brain
was later enabled by
non-invasive brain imaging with
functional magnetic resonance imaging (fMRI) and
positron emission tomography (PET)
\cite{fristen1997imaging}.
Further,
radioactive mapping of neurotransmitter receptors
rendered accessible yet another
local characteristic of neuronal populations
\cite{zilles2009receptor}.
% allude to our many-regions layer in our methods
In the computational era,
automatic clustering methods are increasingly employed to
regionally differentiate the cerebral cortex,
which can partly be more fine-grained than
classical microscopical borders
\cite{behrens03, cbp2015review}.
Today,
high-thoughput approaches enable
ultahigh-resolution 3D models of brain anatomy
at near-cellular scale
\cite{amunts2013bigbrain}.
%
As a crucial common point,
all these methodological approaches
yield neuroscientific findings
that are naturally interpreted according to
non-overlapping, discrete region compartments
as the basic architecture of brain organization.
